%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Flight Software Internship} % Role
    {\href{https://www.teamindus.in/}{Team Indus, Axiom Research Labs Pvt. Ltd.}} % Event
    {Bangalore, India} % Location
    {May 2018 - June 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
      	\item {Engineered Fault Detection, Isolation and Recovery architecture of the spacecraft set to become the world's first privately funded lunar lander.}
        \item {Integrated autonomous fault tolerant systems such as SRAM scrubbing and EDAC traps to correct SEUs and mitigate risk of fatal hardware traps.}
        \item {Established high level on-board FDIR processes for ground intervention which included reset scenarios and configuration management.}
        \item{Formulated strategy to periodically downlink segments of multiple images of executable program and monitor their integrity.}
      \end{cvitems}
    }
    
    \cventry
    {Discrete Control Systems Research} % Job title
    {IIT Kharagpur} % Organization
    {Kharagpur, India} % Location
    {May 2017 - July 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented a discrete time closed loop position controller for magnetic levitation of a metallic ball inside a magnetic field.}
        \item {Obtained an optimal sampling time for 5\% overshoot and 25\% decay ratio for better robustness and tracking compared to previous controllers.}
      \end{cvitems}
    }
    
    \cventry
    {Governor} % Job title
    {\href{https://www.robotix.in/}{Technology Robotix Society}} % Organization
    {Kharagpur, India} % Location
    {March 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheading a team of 45 individuals as the official group of the institute responsible for all robotics activities in and outside of the campus.}
        \item {Pioneered the launch of Makerspace Lab to provide free and open source workspace and resources for the entire student community.}
        \item {Led a 3 tier team to orchestrate Robotix'18, which witnessed participation of 600+ students from 60+ colleges with a budget of INR 0.4 million.}
      \end{cvitems}
    }
    
    

%---------------------------------------------------------
\end{cventries}
