%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Professor In Charge: Dr. Somesh Kumar} % Job title
    {\href{http://www.aerialroboticskgp.org/}{Aerial Robotics Kharagpur}} % Organization
    {Kharagpur, India} % Location
    {March 2016 - March 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Devised navigation and control system for UAV and aerial-ground robot interaction using PID controller and various path planning algorithms.}
        \item {Architected 3 different classes of indigenous autonomous drones as test beds for robotics framework to control Unmanned Aerial Vehicles.}
        \item {Implemented and simulated an algorithm for vision-based landing of a hexacopter on or in vicinity of a mobile ground robot.}
        \item{Researched and built the simulink model of a quadrotor for PID control of its state and velocity on MATLAB to study its dynamics and control}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Professor in Charge: Dr. Alok Kanti Deb} % Job title
    {Hand Gesture Recognition and Tracking} % Organization
    {Kharagpur, India} % Location
    {July 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Executing a Bachelor Thesis Project in the field of computer vision aiming to make real time human-computer interactions more intuitive.}
        \item {Developing a robust marker-less hand gesture recognition system with efficient tracking aimed to replace traditional pointing devices.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Professor in Charge: Sudhirkumar Barai} % Job title
    {Intelligent Water Management System} % Organization
    {Kharagpur, India} % Location
    {April 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Constructed an intelligent water management system to tackle basic faced by smart cities using neural networks and fuzzy logic.}
        \item {The integrated system could control reservoir levels, predict daily and seasonal demand, inspect and sanitize water for efficient results.}
        \item {Peer-reviewed as the second best project among a total of 13 projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
